---
title: "Herbaria in Japan"
author: "Diego T. Vasques"
date: "7/7/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This study gathers information about herbaria in Japan, in hope of creating a comprehensive analysis of how many herbaria exist, where are they located and what kinds of collections they hold.

## Install libraries

```{r}
library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(rgbif)
```

## Import and view data from csv file

```{r}
library(readr)
data <- read_csv("herbaria_data.csv")
View(data)
```

## Plot herbaria on the map 
## Comparing foundation date

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")

class(world)

buff <- 1   #a buffer of one degree around the raster

xmin <- min(data$longitude) - buff
xmax <- max(data$longitude) + buff
ymin <- min(data$latitude) - buff
ymax <- max(data$latitude) + buff

ggplot(data = world) +
  geom_sf(fill = "white") +
  geom_point(data = data, aes(x = longitude, y = latitude, fill = `Founded`, color = `Founded`), color = "black", shape = 21, size = 1.5) + 
  scale_fill_gradient(low = "white", high = "black", limits = c (1850, 2020), breaks = c(1850,1900, 1925, 1950, 1975, 2000, 2020)) +
  scale_color_gradient(low = "white", high = "black", limits = c (1850, 2020), breaks = c(1850,1900, 1925, 1950, 1975, 2000, 2020)) +
  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) + ggtitle('Herbaria foundation year')
```
## Plot herbaria on the map 
## Comparing specimens number

```{r}
world <- ne_countries(scale = "medium", returnclass = "sf")

class(world)

buff <- 1   #a buffer of one degree around the raster

xmin <- min(data$longitude) - buff
xmax <- max(data$longitude) + buff
ymin <- min(data$latitude) - buff
ymax <- max(data$latitude) + buff

ggplot(data = world) +
  geom_sf(fill = "white") +
  geom_point(data = data, aes(x = longitude, y = latitude, fill = `specimens`, color = `specimens`), color = "black", shape = 21, size = 1.5) + 
  scale_fill_gradient(low = "white", high = "black") +
  scale_color_gradient(low = "white", high = "black") +
  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) + ggtitle('Herbaria specimens')
```



